---
title: PMO fields overview 
# format: docx
---

```{r setup, echo=FALSE}
source("../common.R")
```


# Goal  

Creating fields with efforts to be consistent with [MIxS standards](https://genomicsstandardsconsortium.github.io/mixs/). These are the standards that the short read archive (SRA) use to validate metadata upon submission. This also helps to keep data standards to adhere to FAIR (Findable, Accessible, Interoperable, and Reusable). 

Format was developed in order to achieve an efficient/low-weight format that contains the minimum amount of information about a targeted amplicon analysis without losing any important data. Tools are generated around this table to generate certain fields that are important but not necessary to keep constantly stored in this base class (e.g. SNP/INDEL calls). To increase portability and to keep data internally consistent, format was desinged to be contained within a singular file in [JSON format](https://en.wikipedia.org/wiki/JSON) which removes the limitation of storing data only in a tabular format. Output generated from this file can be a table for downstream usage but storing in the flexible JSON format allows storage in non-redundnat organiation (e.g. storing an ID only once while storing other data in lists).

Format is defined by utilizing [LinkML](https://linkml.io/linkml/) to generate a general data scheme which creates various validation outputs like [JSON Schema](https://json-schema.org/) for validation tools. LinkML generates a website for viewing all fields defined in the format, <https://github.com/PlasmoGenEpi/portable-microhaplotype-object>. 

Other notable users of LinkML/MIxS [National Microbiome Data Collaborative Schema](https://github.com/microbiomedata/nmdc-schema)

# Format shcema 


A jsonschema for the format 

```{r}
#| results: asis
#| echo: false

cat(createDownloadLink("portable_microhaplotype_object.schema.json"))

```

