---
title: PMO Examples 
---

{{< fa file >}}

```{r setup, echo=FALSE}
source("../common.R")
```

<script src="https://code.jquery.com/jquery-2.2.2.min.js"></script>

<script>
$(document).ready(function() {
	document.querySelectorAll('.downloadLink').forEach(function(e) { e.setAttribute('download', e.text); });
	document.querySelectorAll('.downloadLink').forEach(function(e) { e.innerHTML = '<i class="fa fa-download"></i>  ' + e.text; });
});
</script>

## Minimum PMO example 

### S_aureus

Contains the PMO for the S. aureus dataset - Furstenau2025_PMO.json.gz. This PMO was contructed from SRA-sourced data[@Furstenau2025-bu]

```{r}
#| results: asis
#| echo: false

cat(createDownloadLink("../pmo_example_datasets/S_aureus/minimum_Furstenau2025_PMO.json.gz"))

```



## Example data from PMO manuscript 

### ANOSPP

Anopheles and Plasmodium data obtained from 4128 mosquito samples from Gabon that were sequenced as part of the ANOSPP (ANOpheles SPecies identification and Plasmodium detection) project[@Makunin2021-pg]

```{r}
#| results: asis
#| echo: false

cat(createDownloadLink("../pmo_example_datasets/ANOSPP/anospp_pmo.json.gz"))

```

### GENE8

Public genomic surveillance data of Plasmodium falciparum from four countries: Eswatini, Namibia, South Africa, and Zambia. This folder contains input files, intermediate PMOs, and processing notebooks [@Aranda-Diaz2025-vx][@Eloff2025-bs][@Nhlengethwa2025-tl][@Raman2025-dk]
```{r}
#| results: asis
#| echo: false

cat(createDownloadLink("../pmo_example_datasets/GENE8/dataset1_pmo_qc_pass.json.gz"))

```

### mips_v_mad4hatter

Contains the PMO containing specimens that were sequenced using both the MAD4HatTeR amplicon sequencing and the DR23K molecular inversion probe (MIP) assay [@Katairo2025-vo]

```{r}
#| results: asis
#| echo: false

cat(createDownloadLink("../pmo_example_datasets/mips_v_mad4hatter/PRJNA1252738_PMO.json.gz"))

```

### E_coli

Contains the PMO for the E. coli dataset - e_coli_coliseq_PMO.json.gz. This PMO was contructed from SRA-sourced data[@Williamson2024-uv] 

```{r}
#| results: asis
#| echo: false

cat(createDownloadLink("../pmo_example_datasets/E_coli/e_coli_coliseq_PMO.json.gz"))

```

### S_aureus

Contains the PMO for the S. aureus dataset - Furstenau2025_PMO.json.gz. This PMO was contructed from SRA-sourced data[@Furstenau2025-bu]

```{r}
#| results: asis
#| echo: false

cat(createDownloadLink("../pmo_example_datasets/S_aureus/Furstenau2025_PMO.json.gz"))

```



### Additional Example data format 

Example created from a study from Mozambique[@Tessema2022-fg] 

<https://academic.oup.com/jid/article/225/7/1227/5897005>

```{r}
#| results: asis
#| echo: false

cat(createDownloadLink("moz2018_PMO.json.gz"))

```

#### From Pf7+ data for the same panel above 


Global data microhaplotypes were constructed by PathWeaver for the same targeted amplicon panel above. This includes approximately 1900 samples.  


```{r}
#| results: asis
#| echo: false

cat(createDownloadLink("PathWeaverHeome1_PMO.json.gz"))

```

